|

### 2021-08-22 dissertation/msc_dissertation.Rmd
Cleaning up code

---
title: |
  | __How analysis strategy affects analysis results__
subtitle: |
  | *Assessing results space and structure of @silberzahn2018 through model specification*
  |
  | MSc Dissertation - DRAFT
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_caption: yes
  word_document: default
linestretch: 1.5
urlcolor: blue
bibliography: references.bib
csl: apa.csl
header-includes:
- \usepackage[ruled,vlined]{algorithm2e}
- \usepackage{float}
- \usepackage{caption}
- \captionsetup[figure]{font={stretch=1}}
---

@@

\begin{algorithm}
\caption{Pseudocode overview--in progress}
\DontPrintSemicolon
\SetAlgoLined
\KwData{Prepared data based on team 23 script}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output} 
$variables$ $\leftarrow$ Define dependent, base variables and covariates \\
$specifications$ $\leftarrow$ Use $variables$ to create matrix containing all possible covariate combinations \\
$formula$ $\leftarrow$ Paste $specifications$ by row and append as column to $specifications$ \\
$formula.ranef; formula.ef$ $\leftarrow$ Separate formulas based on including a random-structure \\
$samlple.ranef; sample.ef$ $\leftarrow$ Random, without replacement, sample from $formula.ranef; formula.ef$
\BlankLine
 initialization\;
  \While{not at end of this document}{
    read current\;
    \eIf{understand}{
      go to next section\;
      current section becomes this one\;
      }{
      go back to the beginning of current section\;
      }
    }
\KwResult{List containing model statistics}
\end{algorithm}

>>>>

---
title: |
  | __How analysis strategy affects analysis results__
subtitle: |
  | *Assessing results space and structure of @silberzahn2018 through model specification*
  |
  | MSc Dissertation
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_caption: yes
  word_document: default
linestretch: 1.5
urlcolor: blue
bibliography: references.bib
csl: apa.csl
header-includes:
- \usepackage[ruled,vlined]{algorithm2e}
- \usepackage{float}
- \usepackage{caption}
- \captionsetup[figure]{font={stretch=1}}
---

@@

\begin{algorithm}
\caption{Pseudocode overview--in progress}
\DontPrintSemicolon
\SetAlgoLined
\KwData{Prepared data based on team 23 script}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output} 
$variables$ $\leftarrow$ Define dependent, base variables and covariates \\
$specifications$ $\leftarrow$ Use $variables$ to create matrix containing all possible covariate combinations \\
$formula$ $\leftarrow$ Paste $specifications$ by row and append as column to $specifications$ \\
$formula.ranef; formula.ef$ $\leftarrow$ Separate formulas based on including a random-structure \\
$samlple.ranef; sample.ef$ $\leftarrow$ Random, without replacement, sample from $formula.ranef; formula.ef$ \\
$wrapper function$ $\leftarrow$ Extracting model statistics and stores them in a list\\
\textbf{tapply}
\BlankLine
 initialization\;
  \While{not at end of this document}{
    read current\;
    \eIf{understand}{
      go to next section\;
      current section becomes this one\;
      }{
      go back to the beginning of current section\;
      }
    }
\KwResult{List containing model statistics}
\end{algorithm}
